The hydra and the rooster

### 2020-08-19 latex/chapter-ordinals.tex
proof simplification in L_alpha
add a new project/exercise
minor corrections

@@

\begin{Coqsrc}
Lemma Successor_succ alpha : Successor (succ alpha) alpha.

Lemma Successor_correct alpha beta : Successor beta alpha <->
                                     beta = succ alpha.
\end{Coqsrc}

We can also check whether an ordinal is a successor:

@@

Lemma succb_correct alpha : succb alpha <-> exists beta,  alpha = succ beta.
\end{Coqsrc}

@@

Let $n$ be some natural number. The segment associated with $n$ is the interval 
$[0,n)\,=\,\{0,1,\dots,n-1\}$.

One may represent the ordinal $n$ by a sigma type.

@@

The order on type \texttt{t $n$} is defined through the projection on \texttt{nat}.

@@

Note that the type \texttt{t 0} is empty, and that \texttt{Program} generates an obligation
for verifying that the constraint $i<n$ is fullfilled when one tries to build the $i$-th ordinal in type \texttt{t $n$}.

@@

>>>>

\index{Coq!Type classes}

@@

\begin{Coqsrc}
Lemma Successor_correct alpha beta : Successor beta alpha <->
                                     beta = succ alpha.
\end{Coqsrc}

We can also check whether an ordinal is a successor by a simple pattern matching:

@@

Lemma succb_correct (alpha : t) :
    succb alpha <->  exists beta: t,   alpha = succ beta.
\end{Coqsrc}

@@

Let $n$ be some natural number. The segment associated with $n$ is the interval 
$[0,n)\,=\,\{0,1,\dots,n-1\}$. 
One may represent the ordinal $n$ by a sigma type.

@@

The order on type (\texttt{t $n$}) is defined through the projection on \texttt{nat}.

@@

Note that the type (\texttt{t 0}) is empty, and that \texttt{Program} generates an obligation
for verifying that the constraint $i<n$ is fullfilled when one tries to build the $i$-th ordinal inside the type (\texttt{t $n$}).

@@

\index{Projects}
\begin{project}
Add to the class \texttt{ON} the requirement that for any $\alpha$ it is decidable whether $\alpha$ is $0$, a successor pr a mimit ordinal.
\end{project}
